### 2019-12-16 tex/ms.tex
more

\begin{figure*}[ht]
        \includegraphics[width=7.0in]{gfa_total_throughput}
    \caption{Total GFA throughput.}
    \label{fig:total_throughput}
\end{figure*}

@@

@@

For this study, we use a series of 22 exposures

@@

@@

\section{PSF-based aperture correction}

@@

Table \ref{tab:zps} lists the zeropoint values obtained in terms of both ADU/s and e-/s on a per-amp basis for all six guide GFA cameras.

@@

\begin{center}
\begin{table}[ht]
\begin{tabular}{c | c | c | c | c}
camera & amp & ZP (total raw ADU/s) & ZP (total e-/s) & assumed gain (e-/ADU, acceptance report) \\ \hline
GUIDE0 & E & 25.714 & 27.079 & 3.516 \\
GUIDE0 & F & 25.689 & 27.063 & 3.545 \\
GUIDE0 & G & 25.654 & 27.067 & 3.673 \\
GUIDE0 & H & 25.695 & 27.078 & 3.574 \\
GUIDE2 & E & 25.633 & 27.045 & 3.668 \\
GUIDE2 & F & 25.612 & 27.035 & 3.708 \\
GUIDE2 & G & 25.654 & 27.067 & 3.673 \\
GUIDE2 & H & 25.627 & 27.057 & 3.733 \\
GUIDE3 & E & 25.652 & 27.063 & 3.669 \\
GUIDE3 & F & 25.679 & 27.058 & 3.560 \\
GUIDE3 & G & 25.615 & 27.061 & 3.785 \\
GUIDE3 & H & 25.623 & 27.052 & 3.729 \\
GUIDE5 & E & 25.626 & 27.052 & 3.718 \\
GUIDE5 & F & 25.630 & 27.062 & 3.741 \\
GUIDE5 & G & 25.636 & 27.066 & 3.733 \\
GUIDE5 & H & 25.621 & 27.066 & 3.787 \\
GUIDE7 & E & 25.569 & 27.036 & 3.863 \\
GUIDE7 & F & 25.664 & 27.063 & 3.629 \\
GUIDE7 & G & 25.494 & 27.011 & 4.043 \\
GUIDE7 & H & 25.512 & 27.008 & 3.967 \\
GUIDE8 & E & 25.615 & 27.047 & 3.740 \\
GUIDE8 & F & 25.601 & 27.048 & 3.793 \\
GUIDE8 & G & 25.699 & 27.090 & 3.601 \\
GUIDE8 & H & 25.652 & 27.072 & 3.698 \\
\end{tabular}
\caption{Summary of measured GFA zeropoints in terms of both ADU/s and e-/s, the latter adopting the lab-measured gains in converting from raw ADU to electrons.}
\label{tab:zps}
\end{table}
\end{center}

>>>>

\begin{figure*}[ht]
        \includegraphics[width=7.0in]{gfa_total_throughput}
    \caption{Total GFA throughput as a function of wavelength.}
    \label{fig:total_throughput}
\end{figure*}

@@

% need to explain 'all' versus 'outer' terminology in rightmost column of gain summary table

@@

For this study, we use a series of 22 exposures. (RA, Dec) =  These exposures were chosen for the following reasons:

\begin{itemize}
\item They were taken during a photometric time period.
\item They were taken in reasonably good seeing -- the FWHM is typically
\item They are taken in a region of high source density
\item They are relatively long GFA exposures (the unique exposure times are 30 seconds and 60 seconds), further improving the density of well-detected sources.
\item Very close to airmass = 1, minimizing impact of any errors in atmospheric transmission component of GFA throughput prediction.
\end{itemize}

% mention "dense fields" program name

@@

In this study we only consider the six in-focus guide cameras, and ignore the data from the four out of focus GFA cameras.

@@

\section{PSF-based Aperture Correction}

@@

Table \ref{tab:zps} lists the zeropoint values obtained in terms of both ADU/s and e-/s on a per-amp basis for all six guide GFA cameras. The zeropoints in terms of ADU are applicable to the raw data --- they do not have any flat fielding baked in. In all cases the zeropoints correspond to total light, night signal within some nominal aperture.

@@

\begin{center}
\begin{table}[ht]
\begin{tabular}{c | c | c | c | c}
camera & amp & ZP (total raw ADU/s) & ZP (total e-/s) & assumed gain (e-/ADU, from acceptance report) \\ \hline
GUIDE0 & E & 25.714 & 27.079 & 3.516 \\
GUIDE0 & F & 25.689 & 27.063 & 3.545 \\
GUIDE0 & G & 25.654 & 27.067 & 3.673 \\
GUIDE0 & H & 25.695 & 27.078 & 3.574 \\
GUIDE2 & E & 25.633 & 27.045 & 3.668 \\
GUIDE2 & F & 25.612 & 27.035 & 3.708 \\
GUIDE2 & G & 25.654 & 27.067 & 3.673 \\
GUIDE2 & H & 25.627 & 27.057 & 3.733 \\
GUIDE3 & E & 25.652 & 27.063 & 3.669 \\
GUIDE3 & F & 25.679 & 27.058 & 3.560 \\
GUIDE3 & G & 25.615 & 27.061 & 3.785 \\
GUIDE3 & H & 25.623 & 27.052 & 3.729 \\
GUIDE5 & E & 25.626 & 27.052 & 3.718 \\
GUIDE5 & F & 25.630 & 27.062 & 3.741 \\
GUIDE5 & G & 25.636 & 27.066 & 3.733 \\
GUIDE5 & H & 25.621 & 27.066 & 3.787 \\
GUIDE7 & E & 25.569 & 27.036 & 3.863 \\
GUIDE7 & F & 25.664 & 27.063 & 3.629 \\
GUIDE7 & G & 25.494 & 27.011 & 4.043 \\
GUIDE7 & H & 25.512 & 27.008 & 3.967 \\
GUIDE8 & E & 25.615 & 27.047 & 3.740 \\
GUIDE8 & F & 25.601 & 27.048 & 3.793 \\
GUIDE8 & G & 25.699 & 27.090 & 3.601 \\
GUIDE8 & H & 25.652 & 27.072 & 3.698 \\
\end{tabular}
\caption{Summary of measured GFA zeropoints in terms of both ADU/s and e-/s, the latter adopting the lab-measured gains in converting from raw ADU to electrons.}
\label{tab:zps}
\end{table}
\end{center}
